\documentclass[a4paper,12pt]{report}
\usepackage[a4paper,left=3cm,right=3cm,tmargin = 3cm]{geometry}
%\linespread{1.6}
\usepackage{leading}
%\leading{1 cm}

\usepackage{xcolor}
\definecolor{orange}{rgb}{1,0.5,0}
\usepackage{amssymb,amsmath,alltt}
\usepackage{graphicx}
\usepackage[latin1]{inputenc}
\usepackage[spanish]{babel}
\usepackage{setspace}
\usepackage{epsfig}
\usepackage{lscape}
\usepackage{subfigure}

\usepackage{longtable}
\usepackage[T1]{fontenc}

\def\changemargin#1#2{\list{}{\topmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist


\DeclareMathOperator{\supess}{supess}
%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath,amssymb,latexsym,amsthm,amscd}
%\usepackage[ansinew]{inpute

\usepackage{times}
%\hyphenation{Python te-ne-mos cons-tan-tes Windows pro-ble-ma re-qui-si-tos o-pe-ra-do-res e-qui-li-brio ob-te-ne-mos ob-te-ni-do di-fe-ren-cial Fa-cul-tad}
%\hyphenation{mo-de-la li-mi-ta-do ge-ne-ral-men-te pue-den es-ta-bi-li-dad des-cri-ba e-xis-ten-ce e-va-l\'u-e a-pro-xi-ma-ci-\'on}
%\hyphenation{a-sin-t\'o-ti-ca-men-te Newton ins-tan-te ge-ne-ra-dor ve-ri-fi-car u-ni-di-men-sio-nal ex-pe-ri-men-ta sa-tis-fa-cer li-ne-al de-sa-rro-llar}
%\hyphenation{mo-di-fi-car}

\usepackage{psfrag}
%\usepackage[hypertex]{hyperref}[2003/11/30]
%\usepackage{lscape}|
%\usepackage{afterpage}
\usepackage{float}
%\usepackage{longtable}
%\usepackage{marvosym}
%\usepackage{titlesec}

\usepackage{verbatim}

\usepackage[usenames,dvipsnames]{pstricks}
\usepackage{epsfig}
\usepackage{pst-grad} % For gradients
\usepackage{pst-plot} % For axes

\newtheorem{theorem}{Teorema}[section]
\newtheorem{acknowledgement}[theorem]{Agradecimiento}
\newtheorem{algorithm}[theorem]{Algoritmo}
\newtheorem{assumption}{Suposici\'on}[section]
\newtheorem{axiom}[theorem]{Axioma}
\newtheorem{case}[theorem]{Caso}
\newtheorem{claim}[theorem]{Afirmaci\'{o}n}
\newtheorem{conclusion}[theorem]{Conclusi\'{o}n}
\newtheorem{condition}[theorem]{Condici\'{o}n}
\newtheorem{conjecture}[theorem]{Conjetura}
\newtheorem{corollary}[theorem]{Corolario}
\newtheorem{criterion}[theorem]{Criterio}
\newtheorem{definition}[theorem]{Definici\'{o}n}
\newtheorem{exercise}[theorem]{Ejercicio}
\newtheorem{lemma}[theorem]{Lema}
\newtheorem{notation}[theorem]{Notaci\'{o}n}
\newtheorem{problem}[theorem]{Problema}
\newtheorem{proposition}[theorem]{Proposici\'{o}n}
\newtheorem{remark}{Oservaci\'on}
\newtheorem{solution}[theorem]{Soluci\'{o}n}
\newtheorem{summary}[theorem]{Resumen}
%\newenvironment{demos}[1][Demos]{\noindent\textbf{#1.} }

\newtheorem{def_app}{Definici\'{o}n}
\newtheorem{lem_app}{Lema}[section]
\newtheorem{teo_app}{Teorema}
\newtheorem{demos_lem}[]{Demostraci\'{o}n}
\newtheorem{demos}[]{Demostraci\'{o}n}
\newtheorem{coro}{Corolario}
\newtheorem{demos_coro}[]{Demostraci\'{o}n}

%\newenvironment{prueba}[1][Prueba]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
%\newtheorem
\newenvironment{prueba}[1][Demostraci\'{o}n]{\noindent\textbf{#1.} }

%%%%%%%%%%%%%%%%%%%%%%%%%


\input{./thesinput.tex}


%\includeonly{aprobacion,catalografica,dedicatoria,resumen,agradecimientos,3.capitulo01,3.capitulo02}

\begin{document}

\makeatletter
\def\@roman#1{\romannumeral #1}
\makeatother

\pagenumbering{roman}\setcounter{page}{2}    

\input{title}
\clearemptydoublepage
\include{aprobacion}
\clearemptydoublepage
\include{catalografica}
%\clearemptydoublepage
\include{dedicatoria}
%\clearemptydoublepage
\include{agradecimientos}

%\leading{0.8 cm}
\clearemptydoublepage
\include{resumen}
\clearemptydoublepage
\include{abstract}

%\leading{1 cm}
\clearemptydoublepage
\tableofcontents

\include{prodvectorial}
\include{ch1}
%\include{3.apendice3}
%\clearemptydoublepage
%Otros apendices
%\bibliographystyle{abbrv}
%\bibliography{myblib}
\begin{thebibliography}{}

\bibitem{A-P}\label{AP}
√Ålvarez, F.; Peypouquet, J.
\newblock{\em Introducci\'on a la Teor\'ia de Semigrupos}
\newblock Apuntes para la III Escuela de Verano; Universidad de Chile, 2003.

\bibitem{A-H}\label{AH}
Atkinson, K.; Han, W.
\newblock{\em Theoretical Numerical Analysis: a functional analysis framework}
\newblock Texts in applied mathematics; 39.

\bibitem{B-F}\label{BF}
Burden, R.; Faires, J.
\newblock{\em An\'alisis Num\'erico}
\newblock Thomson Learning, Mexico, D.F. 2002.

\bibitem{Br}\label{Br}
Brezis, H.
\newblock{\em Analyse fonctionnelle: the\'orie et applications}
\newblock Masson, Paris, 1983

\bibitem{Ca}\label{Ca}
Carbajal P., Efra\'in
\newblock{\em Una clase de algor\'itmos de alta precisi\'on para un sistema acoplado}.
\newblock PESQUIMAT, Revista de la Unidad de Post Grado - UNMSM, Vol. 3, Nro. 1, Junio 1999, pag. 1-14.

\bibitem{Cod}\label{Cod}
Code\c{c}o Coelho, F.
\newblock{\em Computa\c{c}√£o cient\'ifica com Python : Uma introdu\c{c}√£o √  programa\c{c}√£o para cientistas}
\newblock Petr\'opolis - RJ, 2007.

\bibitem{Cun}\label{Cun}
Cunha, C. A.
\newblock{\em Semigrupos Aplicados a Sistemas Dissipativos em EDP}
\newblock Florian\'opolis, SC: SBMAC, 2007.


\bibitem{Daf}\label{Daf}
Dafermos, C. M.
\newblock{\em On the existence and the asymptotic stability of solution to the equatios of linear thermoelasticity}
\newblock Arch. Rational Mech. Anal., 29 (1968), 241-271.

\bibitem{Hoff}\label{Hoff}
Hoffman, Joe D.
\newblock{\em Numerical methods for engineers and scientists}
\newblock Marcel Dekker, Inc. 2001.

\bibitem{Ji-Rac}\label{Ji-Rac}
Jiang, Song; Racke, Reinhard
\newblock{\em Evolution Equations in Thermoelasticity}.
\newblock Chapman \& Hall/CRC. 2000.

\bibitem{Jo}\label{Jo}
Johnson, A.
\newblock{\em The Fundamental Theorem of Numerical Analysis}.
\newblock 2006.

\bibitem{Kin}\label{Kin}
Kincaid, David; Ward, E.   
\newblock{\em Numerical analysis : mathematics of scientific computing}
\newblock Brooks/Cole Publishing Company. 1990.

\bibitem{Kr}\label{Kr}
Kreyszig, E.
\newblock{\em Introductory functional analysis with applications.}
\newblock John Wiley e Sons, 1978.

\bibitem{Mu}\label{Mu}
Mu\~noz Rivera, J.E.
\newblock{\em Semigrupos e Equa\c{c}\~{o}es Diferenciais Parciais}
\newblock Laborat\'orio Nacional de Computa\c{c}√£o Cient\'ifica, Textos de p\'os gradua\c{c}√£o.

\bibitem{Mu-1}\label{Mu1}
Mu\~noz Rivera, J.E.
\newblock{\em Energy decay rates in linear thermoelasticity}
\newblock Funkcialaj Ekvacioj, 35(1) (1992), 19-30.

\bibitem{Pa}\label{Pa}
Pazy, A.
\newblock{\em Semigroups of linear operators and applications to partial differential equations}
\newblock Springer-Verlag, New York 1983.

\bibitem{Pe-Mz}\label{Pe-Mz}
Pereira, D.C.; Menzala, G.P.
\newblock{\em Exponential decay of solutions in thermoelasticity}
\newblock Comp. Appl. Math., 8(1989), 192-204.

\bibitem{Ra}\label{Ra}
Racke, R.
\newblock{\em Exponential decay for a class of initial boundary value problems in thermoelasticity}
\newblock Comp. Appl. Math., 12(1993), 67-80.

\bibitem{R-K}\label{RK}
Richtmyer, R.D.; Morton, K.W.
\newblock{\em Difference Methods for Initial Value Problems}
\newblock Interscience Publishers, New York, 1967.

\bibitem{St-Bu}\label{StBu}
Stoer, J.; Bulirsch, R.
\newblock{\em Introduction to numerical analysis}
\newblock Springer-Verlag New York, Inc. 1992.

\bibitem{Yo}\label{Yo}
Yosida, K√¥saku 
\newblock{\em Functional Analysis}.
\newblock Splinger-Verlag, Berlin Heidelberg New York 1980.

\bibitem{Zua}\label{Zua}
Zuazua, Enrique 
\newblock{\em T\'opicos de An\'alisis Num\'erico}.
\newblock Departamento de Matem\'aticas, Universidad Aut\'onoma. Madrid, Espa\~na.

% Brezis -- kreyzig




\end{thebibliography}


\clearemptydoublepage
\end{document}